Bayesian statistics for repeated measures

### 2020-10-15 Manuscripts/Manuscript_AM_v1.Rmd
Started writing intro

---
title: "Bayesian statistics for repeated measures"
author: "Ariel Mundo, John Tipton, Timothy Muldoon"
subtitle: Their application and use in biomedical research
output: 
    html_document: default
    word_document:
     reference_docx: docx_template.docx
    #pdf_document: default
bibliography: refs.bib
---
Paper outline

@@

1.

Biomedical research often uses longitudinal studies to analyze tumor response [@vishwanath2009].

>>>>

---
title: "Bayesian statistics for repeated measures"
author: "Ariel Mundo, John Tipton, Timothy Muldoon"
subtitle: Their application and use in biomedical research
output: 
    html_document: default
    css: style.css
    word_document:
     reference_docx: docx_template.docx
mainfont: Times New Roman
    #pdf_document: default
bibliography: refs.bib
biblio-style: apalike
link-citations: yes
---

Paper outline

@@

The study of the temporal changes in a variable of interest is a question that has been analyzed extensively in biomedical research. Typically, measurements are taken across multiple timepoints on the same subject(s) within a group.  Examples of this type of approach include clinical studies on cancer breast and neck cancer[@sio2016;@kamstra2015], tumor response[@roblyer2011;@tank2020;@pavlov2018;@demidov2018], antibody expression[@ritter2001;@roth2017], and cell metabolism[@jones2018;@skala2010]. Whereas this type of study presents advantages over a cross-sectional study in the number of subjects required to achieve a certain statistical power, and in its ability 
[@chavalarias2016]

[@vishwanath2009].

### Longitudinal vs
